`flippant` --- An `R` package for the automated analysis of dithionite scramblase

### 2016-07-16 inst/manuscript/manuscript.rmd
Update citations;

To interrogate scramblases as a functional class of proteins, a biochemical
assay was developed suited to characterize scramblase activity of purified 
proteins and protein extracts based on the reconstitution of scramblases or 
candidate proteins into preformed synthetic liposomes that contain trace amounts
of nitrobenzoxadiazole (NBD) labeled fluorescent lipids [@chang_chemical_2004].
Upon addition of membrane--impermeable reducing agents such as dithionite to 
these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase--free liposomes accordingly quickly drops to approximately 50% of the 
initial value. However, for proteoliposomes reconstituted with proteins 
conferring a scramblase activity, fluorescence disappears entirely, as
fast scramblase--mediated equilibration between outer (exposed) and inner
(protected) leaflet of the bilayer renders all fluorescent lipids
accessible to reduction. By titration of the protein amount reconstituted into
the liposome membranes it is thus possible to characterize scramblases and probe
their activity. Beyond the identification of scramblase activities in crude 
membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the 
assay has also been used to characterize the stoichiometry of scramblase 
homo--multimers reconstituting into the proteoliposomes 
[@ploier_perturbed_submitted] and probe the ATP--dependence of flippases, 
molecules that under energy--consumption flip lipids against a concentration 
gradient between bilayer leaflets [@soupene_atp8a1_2008].

Starting with the identification of baseline and post--reduction fluorescence 
from fluorometer--generated spectra, via the calculation of the underlying 
statistics and through publication--grade representation of the results, data 
analysis in the context of this assay has until now involved an extensive series
of manual steps, at most supported by spreadsheet calculation facilities
[see @menon_opsin_2011;@goren_constitutive_2014;@ploier_perturbed_submitted for
extensive step--wise discussion].
Based on the `R` free software environment for statistical computing and 
graphics [@r_core_team_r:_2015] and prominently drawing on the power and 
elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
provide `flippant`, a package that comprehensively, fast and reproducibly covers
all data analysis and graphing needs from raw fluorescence spectra produced by 
scramblase assays. A simple parametrizing spreadsheet is the sole required user 
input.

# Availablility and Implementation
`flippant` has been implemented in `R` [@r_core_team_r:_2015] and integrated 
into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
within a functional `R` environment:

@@

Based on @menon_opsin_2011, @goren_constitutive_2014 as well as
@ploier_perturbed_submitted and largely keeping with nomenclature used therein,
data is processed as follows. Input is format checked and defaults are injected
for facultative parameters/columns as appropriate. 
Fluorescence spectra are parsed. This includes algorithmic determination of when 
dithionite was added to the sample using peak detection by continuous wavelet
transformation as implemented in the `wmtsa` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
Acquisition time is aligned for all spectra in the data set such that the zero 
time point henceforth corresponds to the time of addition. 
Pre--dithionite--addition baseline fluorescence $F_{\text{baseline}}$ is 
determined for each spectrum by averaging (median) over the ten values preceding
dithionite addition. Post--dithionite--addition minimum fluorescence 
$F_{\text{min}}$ is analogously calculated from the last ten data points before 
(and including) a default 400 s or the time point of measurement supplied by the
user in the parameter spreadsheet. $F_{\text{min}}$ is volume--corrected based on
supplied reaction volumes with and without dithionite and for each spectrum/data
point a fluorescence reduction is calculated as follows:
$$
y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
$$
A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes--only/no--protein control and the probability $P_{\geq 1}$ for a 
liposome to contain at least one scramblase molecules is calculated using
$$
P_{\geq 1} = \frac{(y - y_0)}{(y_{\text{max}} - y_0)}
$$
where $y$ is the relative fluorescence reduction for the proteoliposome 
measurement and $y_0$ for a measurement of protein--free liposomes. 
$y_{\text{max}}$ refers to either the maximal $y$ in the experiment or is 
derived from a monoexponential fit to the data (default) as a precaution for the 
case where the protein/phospholipid titration did not reach the plateau of the 
saturation curve. The behavior is adjustable using the `scale_to` parameter of 
the corresponding functions (see below). Next a monoexponential curve is fitted
to the relationship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
(mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$. By
default and following @ploier_perturbed_submitted, PPR is scaled by a factor of
0.65 to account for a fraction of the vesicle pool used that is refractory to
scramblase reconstitution. This behavior can be modified using the 
`ppr_scale_factor` parameter and avoided alltogether setting it to `NULL`.

@@

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`). The behavior of the function
may be adjusted to use scramblase--mediated fluorescence reduction normalized to
either the maximum measurement in the series (`scale_to = "data"`) or the
plateau of an exponential fit to it (`scale_to = "model"`; default; for
reasoning see above). `ppr_scale_factor` allows for the modification of scaling
to account for a pool of vesicles that is scramblase--inaccessible (see above).
The formula to which the data is fitted has evolved over time and `flippant`
supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_perturbed_submitted; default; `generation_of_algorithm = 2`), which
takes into account the size distribution of the liposome polulation used and
thus also requires parameters for liposome radius and its standard deviation 
(`r_bar` and `sigma_r_bar`, respectively; in nm, both). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis
(`split_by_experiment = FALSE`) or treated separately
(`split_by_experiment = TRUE`; see below for example usage). The
`force_through_origin` parameter may be used to employ a fit with more degrees
of freedom. While the non--default `force_through_origin = FALSE` allows for a
better fit to some experimental data, its mechanistic implications are unclear.

@@

# Case Study
*Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
cases of which is linked to mutant forms of the G--protein coupled receptor 
rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
we hypothesized that a class of enigmatic rhodopsin mutations, which are known
to cause *retinitis pigmentosa* yet do not display the commonly associated 
molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
transducin activation, may in fact be impacted in their scramblase activity.
This hypothesis was disproved when tested using the dithionite scramblase assay
among other techniques. However, the same set of experiments pointed at a defect 
in rhodopsin dimerization prior to insertion into liposomes, generating the new 
hypothesis that the mutations may cause disease by interfering with the highly 
ordered quarternary structure of the molecule in the retina 
[@ploier_perturbed_submitted].

@@

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_perturbed_submitted.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- tmpDir %>%
  file.path("inputTable.txt") %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
flippant::scramblase_assay_traces(
  x,
  time_max_sec = 350)
```

@@

```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 2 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2 %<>% add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(x) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
figure2
```

@@

Figure 2A emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C--F by
@ploier_perturbed_submitted, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 2B:

@@

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- flippant::scramblase_assay_stats(
    x, split_by_experiment = FALSE) %>%
  dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  magrittr::set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  magrittr::extract2("Experimental Series") %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results %>%
  magrittr::extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_perturbed_submitted.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

The resulting values for the fit constant $\alpha$ correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_perturbed_submitted (Table S2), where $\alpha
\times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
in @ploier_perturbed_submitted that the mutant rhodopsins investigated are
reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

@@

With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
R as an environment for statistical computing and graphics 
[@r_core_team_r:_2015], scientists can quickly analyse such data and arrive at 
publication--grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
`r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (median; 
$\text{IQR}=`r analysis_timing_iqr`~\text{s}$; $n=`r analysis_timing_n`$).

>>>>

To interrogate scramblases as a functional class of proteins, a biochemical
assay was developed suited to characterize scramblase activity of purified 
proteins and protein extracts based on the reconstitution of scramblases or 
candidate proteins into preformed synthetic liposomes that contain trace amounts
of nitrobenzoxadiazole (NBD) labeled fluorescent lipids [@chang_chemical_2004].
Upon addition of membrane--impermeable reducing agents such as dithionite to 
these liposomes, fluorophores in the external leaflet are quenched and fluorescence in scramblase--free liposomes accordingly quickly drops to approximately 50% of the 
initial value. However, for proteoliposomes reconstituted with proteins 
conferring a scramblase activity, fluorescence disappears entirely, as
fast scramblase--mediated equilibration between outer (exposed) and inner
(protected) leaflet of the bilayer renders all fluorescent lipids
accessible to reduction. By titration of the protein amount reconstituted into
the liposome membranes it is thus possible to characterize scramblases and probe
their activity. Beyond the identification of scramblase activities in crude 
membrane preparations [@chang_chemical_2004;@rajasekharan_flip-flop_2011] and 
functional validation of candidate scramblases [@menon_opsin_2011;@malvezzi_ca2-dependent_2013;@goren_constitutive_2014], the 
assay has also been used to characterize the stoichiometry of scramblase 
homo--multimers reconstituting into the proteoliposomes 
[@ploier_dimerization_2016] and probe the ATP--dependence of flippases, 
molecules that under energy--consumption flip lipids against a concentration 
gradient between bilayer leaflets [@soupene_atp8a1_2008].

Starting with the identification of baseline and post--reduction fluorescence 
from fluorometer--generated spectra, via the calculation of the underlying 
statistics and through publication--grade representation of the results, data 
analysis in the context of this assay has until now involved an extensive series
of manual steps, at most supported by spreadsheet calculation facilities
[see @menon_opsin_2011;@goren_constitutive_2014;@ploier_dimerization_2016 for
extensive step--wise discussion].
Based on the `R` free software environment for statistical computing and 
graphics [@r_core_team_r:_2016] and prominently drawing on the power and 
elegance of the `ggplot2` plotting system [@wickham_ggplot2_2009], we here 
provide `flippant`, a package that comprehensively, fast and reproducibly covers
all data analysis and graphing needs from raw fluorescence spectra produced by 
scramblase assays. A simple parametrizing spreadsheet is the sole required user 
input.

# Availablility and Implementation
`flippant` has been implemented in `R` [@r_core_team_r:_2016] and integrated 
into the `bioconductor` collection of tools for biomedical data analysis [@huber_orchestrating_2015]. It is thus install-- and loadable as follows from 
within a functional `R` environment:

@@

Based on @menon_opsin_2011, @goren_constitutive_2014 as well as
@ploier_dimerization_2016 and largely keeping with nomenclature used therein,
data is processed as follows. Input is format checked and defaults are injected
for facultative parameters/columns as appropriate. 
Fluorescence spectra are parsed. This includes algorithmic determination of when 
dithionite was added to the sample using peak detection by continuous wavelet
transformation as implemented in the `wmtsa` package [@percival_wavelet_2000;@constantine_wmtsa:_2013]. 
Acquisition time is aligned for all spectra in the data set such that the zero 
time point henceforth corresponds to the time of addition. 
Pre--dithionite--addition baseline fluorescence $F_{\text{baseline}}$ is 
determined for each spectrum by averaging (median) over the ten values preceding
dithionite addition. Post--dithionite--addition minimum fluorescence 
$F_{\text{min}}$ is analogously calculated from the last ten data points before 
(and including) a default 400 s or the time point of measurement supplied by the
user in the parameter spreadsheet. $F_{\text{min}}$ is volume--corrected based on
supplied reaction volumes with and without dithionite and for each spectrum/data
point a fluorescence reduction is calculated as follows:
$$
y_{\text{raw}} = 1 - \frac{F_{\text{min}}}{F_{\text{baseline}}}
$$
A relative fluorescence reduction $y$ is calculated scaled to a (required) liposomes--only/no--protein control and the probability $P_{\geq 1}$ for a 
liposome to contain at least one scramblase molecules is calculated using
$$
P_{\geq 1} = \frac{(y - y_0)}{(y_{\text{max}} - y_0)}
$$
where $y$ is the relative fluorescence reduction for the proteoliposome 
measurement and $y_0$ for a measurement of protein--free liposomes. 
$y_{\text{max}}$ refers to either the maximal $y$ in the experiment or is 
derived from a monoexponential fit to the data (default) as a precaution for the 
case where the protein/phospholipid titration did not reach the plateau of the 
saturation curve. The behavior is adjustable using the `scale_to` parameter of 
the corresponding functions (see below). Next a monoexponential curve is fitted
to the relationship of $P_{\geq 1}$ to the protein to phospholipid ratio (PPR; 
(mg/mmol)), providing the scramblase--characterizing fit factor $\alpha$. By
default and following @ploier_dimerization_2016, PPR is scaled by a factor of
0.65 to account for a fraction of the vesicle pool used that is refractory to
scramblase reconstitution. This behavior can be modified using the 
`ppr_scale_factor` parameter and avoided alltogether setting it to `NULL`.

@@

allows for the complete generation of the PPR plot in publication quality from
the user assembled spreadsheet of input data (`x`). The behavior of the function
may be adjusted to use scramblase--mediated fluorescence reduction normalized to
either the maximum measurement in the series (`scale_to = "data"`) or the
plateau of an exponential fit to it (`scale_to = "model"`; default; for
reasoning see above). `ppr_scale_factor` allows for the modification of scaling
to account for a pool of vesicles that is scramblase--inaccessible (see above).
The formula to which the data is fitted has evolved over time and `flippant`
supports both the original (@menon_opsin_2011; @goren_constitutive_2014; `generation_of_algorithm = 1`), as well as the more recent iteration (@ploier_dimerization_2016; default; `generation_of_algorithm = 2`), which
takes into account the size distribution of the liposome polulation used and
thus also requires parameters for liposome radius and its standard deviation 
(`r_bar` and `sigma_r_bar`, respectively; in nm, both). The
`split_by_experiment` argument is used to indicate whether independent
experiments are integrated into a single analysis
(`split_by_experiment = FALSE`) or treated separately
(`split_by_experiment = TRUE`; see below for example usage). The
`force_through_origin` parameter may be used to employ a fit with more degrees
of freedom. While the non--default `force_through_origin = FALSE` allows for a
better fit to some experimental data, its mechanistic implications are unclear.

@@

# Case Study
*Retinitis pigmentosa* is a degenerative disease of the retina, the majority of 
cases of which is linked to mutant forms of the G--protein coupled receptor 
rhodopsin [@mendes_mechanisms_2005]. Motivated by the recent discovery that 
opsin/rhodopsin has scramblase activity [@menon_opsin_2011;@goren_constitutive_2014],
we hypothesized that a class of enigmatic rhodopsin mutations, which are known
to cause *retinitis pigmentosa* yet do not display the commonly associated 
molecular phenotypes of impaired binding of retinal, folding and/or trafficking or 
transducin activation, may in fact be impacted in their scramblase activity.
This hypothesis was disproved when tested using the dithionite scramblase assay
among other techniques. However, the same set of experiments pointed at a defect 
in rhodopsin dimerization prior to insertion into liposomes, generating the new 
hypothesis that the mutations may cause disease by interfering with the highly 
ordered quarternary structure of the molecule in the retina 
[@ploier_dimerization_2016].

@@

```{r figure1_creation, echo = FALSE, fig.height = 4, fig.cap = "**`flippant`--based plotting of spectral traces underlying the data in Figure 4C--F from @ploier_dimerization_2016.** See text for command and details."}
# Plot spectral traces (Figure 1)
x <- tmpDir %>%
  file.path("inputTable.txt") %>%
  flippant:::read_scramblase_input_file()
x[["Path"]] <- file.path(tmpDir, x[["Path"]])
flippant::scramblase_assay_traces(
  x,
  time_max_sec = 350)
```

@@

```{r figure2_creation, echo = FALSE, warning = FALSE, message = FALSE, fig.cap = "**`flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** (A) and (B) show protein to phospholipid ration (PPR) plots for the data using a x--axis trimmed to a maximum value of 3 (see text for details). In (A) data is separately plotted for independent experiments, while (B) combines all data points, aiming for reliability of fit. 'adj. PPR' indicates that the measure has been scaled to account for a vesicle pool refractory to flippase reconsitution."}
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 1,
  panel = flippant::scramblase_assay_plot(x) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])))
figure2 %<>% multipanelfigure::add_panel(
  top_panel = 2,
  panel = flippant::scramblase_assay_plot(x, split_by_experiment = FALSE) + 
    ggplot2::theme_bw() + 
    ggplot2::xlim(0, 3) + 
    ggplot2::xlab(expression("adj. PPR"~~("mg"/"mmol"))) +
    ggplot2::ylab(expression(P[{phantom()>=1}])) +
    ggplot2::facet_wrap(c("`Experimental Series`"))+
    ggplot2::guides(colour = "none"))
figure2
```

@@

Figure 2A emphasizes reproducibility between independent experiments
("Experiment 1" and "Experiment 2") on the four probed rhodopsins. Forgoing
reproducibility analysis in favor of a potentially more reliable result and
following more closely the analysis in Figure 4C--F by
@ploier_dimerization_2016, a single fit may be performed for the combined data
from all experiments as follows, resulting in Figure 2B:

@@

```{r analysis_tabular_output, echo = FALSE}
ppr_results <- flippant::scramblase_assay_stats(
    x, split_by_experiment = FALSE) %>%
  dplyr::mutate(`Fit Constant` = round(`Fit Constant` * 10^4, 2)) %>%
  magrittr::set_names(c("Experimental Series", "Fit Constant ($\\times 10^4$)"))
ppr_results_names <- ppr_results %>%
  magrittr::extract2("Experimental Series") %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Experimental Series`, n = 1))
ppr_results_alpha_print <- ppr_results %>%
  magrittr::extract2("Fit Constant ($\\times 10^4$)") %>%
  round(2) %>%
  head(n = nrow(ppr_results) - 1) %>%
  paste(collapse = ", ") %>%
  paste("and") %>%
  paste(tail(ppr_results$`Fit Constant ($\\times 10^4$)`, n = 1))
knitr::kable(
  ppr_results,
  row.names = FALSE,
  caption = "**Tabular output of `flippant`--based reanalysis of data in Figure 4C--F from @ploier_dimerization_2016.** An plain text--version of this output is produced by calling `scramblase_assay_stats`.")
```

The resulting values for the fit constant $\alpha$ correspond with
`r ppr_results_alpha_print` for `r ppr_results_names`, respectively, well to the
prior manual analysis by @ploier_dimerization_2016 (Table S2), where $\alpha
\times 10^4 \approx 16$ was reported for mutant and $\alpha \times 10^4 \approx
7$ for wild type rhodopsin. Based on the manual analysis of the data we conclude
in @ploier_dimerization_2016 that the mutant rhodopsins investigated are
reconstituted into proteoliposomes in monomeric form, contrary to the wild type,
which is reconstituting as a homodimer. 
`flippant` analysis of the data shows identical trends and close matches of the
results, supporting identical conclusions.

@@

With `flippant` we present an integrated solution for data analysis in the 
context of dithionite scramblase assays. Requiring only basic familiarity with 
R as an environment for statistical computing and graphics 
[@r_core_team_r:_2016], scientists can quickly analyse such data and arrive at 
publication--grade graphics that offer extensive facilities for individual 
optimization and adaptation [@wickham_ggplot2_2009]. On a laptop system with 
`r parallel::detectCores()` cores and 8 GB RAM (no SSD), running `Linux` and 
`R` version `r paste(R.version[c("major","minor")], collapse = ".")`, the
statements generating equivalents to the plots and calculations presented here
take a mere `r analysis_timing_median` seconds (median; 
$\text{IQR}=`r analysis_timing_iqr`~\text{s}$; $n=`r analysis_timing_n`$).
